### 2014-08-11 fundamentals/intro.tex
addresses @gidden comment about 'full detail'

In nuclear fuel cycle simulation it is necessary to calculate and optimize 
nuclear process physics, facility deployment, material routing, etc.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to full detail industrial 
models.

@@

>>>>

In nuclear fuel cycle simulation, it is necessary to calculate and optimize 
nuclear process physics, facility deployment, and material routing in order to 
capture overall fuel cycle performance metrics.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to very high-fidelity industrial 
models.

@@

We expect that there are a number of types of users and developers who will 
interact with the Cyclus framework. Those people fall into a number of 
categories. All such people benefit from the modular architecture.

<modified-open-source collaboration diagram>
